\LARGE \bf A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-03-29 paper.tex
citation on computer generated data

The international movement towards developing autonomous vehicle technologies has raised concerns in many spheres of society: from legal perspectives \cite{Pattinson2020} to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing. Over the
last decade, some emphasis has been made on the need for these vehicles to reduce road collisions and reckless driving. However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets. Currently, this type of data is most effectively created through computer generated scenarios due to the dangerous and costly nature of road collisions. We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods. Futher, we present an aggregated dataset that we have produced using our pipeline which includes egocentric vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.

@@

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}" contains a description of the video as scraped from the video hosting website
  \item "\texttt{state}" is a string that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}" contains the site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}" is an object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}" is a string that represents the type of the video
  \item "\texttt{url}" is the url that the video was fetched from
  \item "\texttt{is\_split\_url}" is a boolean that is true if all of the frames of the video are covered in this metadata item and false if no
  \item "\texttt{enum\_tags}" is a list of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{bb\_fields}" contains all bounding-box specific data.
  \begin{itemize}
    \item "\texttt{collision\_locations}" a list of frame numbers indicating the collision start frames
    \item "\texttt{resolution}" A list with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
    \item "\texttt{objects}" Is a list of all of the bounding boxes for each object in the video. An object being either a vehicle or pedestrian. Within each object, there is metadata specific to that object.
    \begin{itemize}
      \item "\texttt{id}" Is a  unique numerical identifier that represents this object
      \item "\texttt{bboxes}" Is a list of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
      \item "\texttt{class}" Represents the class of the object, and will be one of "car", "truck", "motorcycle", "van", "pedestrian", "bus"
      \item "\texttt{has\_collision}" Is a boolean that is true if the object is in a collision, false otherwise
    \end{itemize}
  \end{itemize}
\end{itemize}`

>>>>

The international movement towards developing autonomous vehicle technologies has raised concerns in many spheres of society: from legal perspectives \cite{Pattinson2020} to ethical dilemmas; from control theory to safety engineering; from cybersecurity to realtime computing. Over the
last decade, some emphasis has been made on the need for these vehicles to reduce road collisions and reckless driving. However, research into collision avoidance has been slowed down by the lack of egocentric footage datasets. Currently, this type of data is created through computer generated scenarios \cite{Kim_Lee_Hwang_Suh_2019} due to the dangerous and costly nature of road collisions. We provide a pipeline to assemble datasets of real events that have been published online to complement already existing methods. Futher, we present an aggregated dataset that we have produced using our pipeline which includes egocentric vehicle footage from all over the world subject to varying visibilities, varying weather conditions, and varying settings.

@@

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}" contains a description of the video as scraped from the video hosting website
  \item "\texttt{state}" is a string that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}" contains the site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}" is an object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}" is a string that represents the type of the video
  \item "\texttt{url}" is the url that the video was fetched from
  \item "\texttt{is\_split\_url}" is a boolean that is true if all of the frames of the video are covered in this metadata item and false if no
  \item "\texttt{enum\_tags}" is a list of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{bb\_fields}" contains all bounding-box specific data.
  \begin{itemize}
    \item "\texttt{collision\_locations}" a list of frame numbers indicating the collision start frames
    \item "\texttt{resolution}" A list with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
    \item "\texttt{objects}" Is a list of all of the bounding boxes for each object in the video. An object being either a vehicle or pedestrian. Within each object, there is metadata specific to that object.
    \begin{itemize}
      \item "\texttt{id}" Is a  unique numerical identifier that represents this object
      \item "\texttt{bboxes}" Is a list of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
      \item "\texttt{class}" Represents the class of the object, and will be one of "car", "truck", "motorcycle", "van", "pedestrian", "bus"
      \item "\texttt{has\_collision}" Is a boolean that is true if the object is in a collision, false otherwise
    \end{itemize}
  \end{itemize}
\end{itemize}
